Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-04-05 paper/paper-nature_format.qmd
added to next steps

One important contribution would be to take advantage of similar records that exist for the Senate over this same period and add them to our database. The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar.

Earlier House of Representatives records also exist. In some cases it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning.

>>>>

One important contribution would be to take advantage of similar records that exist for the Senate over this same period and add them to our database. The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar, making many elements of our code and methodology applicable to this work.

Earlier House of Representatives records also exist, and would be valuable to include in future versions of our database. In some cases however it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning and likely additional script development to account for changes in structural formatting.

Having completed this work, we recognize components of our scripts which could be developed in a more computationally efficient manner such as our approach to splitting interjections and filling in MP details. In future, it would be beneficial to review our methodological approach to these steps, and consider approaches which are more concise where appropriate.
